Discussion

### 2023-03-16 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added conclusion

In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e. whether they would show trait character.
In other words, do the values we calculate represent a stable value within the individual?
This conclusion cannot be drawn from the present study alone.
The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
By definition, this represents a state.
As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We belief that these goals, factors and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals[@Tamir2016].
Wilms and colleagues[@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
It should also be noted that the computation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
Therefore, SVs could vary if other reference strategies are used.
It is conceivable that the subjective values are likely to correlate very highly in situations with similar demands and goals. 
They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
However, our data are not suitable for answering this question.
In future, the SVs should therefore be collected in several similar situations. 
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

@@

>>>>

In order to further assess the relevance of the calculated individual SVs, it would be important to know how stable the values are, i.e. whether they would show trait character.
In other words, do the values we calculate represent a stable value within the individual?
This conclusion cannot be drawn from the present study alone.
The individual SVs computed in our CAD paradigm were assessed in the laboratory in a single situation.
By definition, this represents a state.
As previously noted, personal regulation goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We belief that these goals, factors and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also means that SVs should differ according to situational factors (e.g., intensity of stimuli).
It also must be taken into account which ER goals the individuals are pursuing in a particular situation.
In our laboratory setting, participants pursue mainly prohedonic goals, but certainly not social goals[@Tamir2016].
Wilms and colleagues[@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary strongly among events and situations.
In another situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, another strategy might appear more helpful and thus have a higher SV.
It should also be noted that the computation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
Therefore, SVs could vary if other reference strategies are used.
It is conceivable that the subjective values are likely to correlate very highly in situations with similar demands and goals. 
They would thus reflect habits, or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
The other way round, of course, it is also conceivable that such habits influence the internal formation of these subjective values.
However, our data are not suitable for answering this question.
In future, the SVs should therefore be collected in several similar situations. 
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

@@

In order to cope with changing emotional demands, individuals can flexibly select and apply strategies from their repertoire[@Bonanno2013;@Aldao2015].
The strategy that is most suitable for dealing with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
The combination of influencing factors should be reflected in subjective values, which are formed for all alternatives and serve as a basis for decision-making.
So far, such subjective values for ER strategies have not been determined.
Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
This provides a more detailed investigation of factors influencing the internal generation of these SVs of ER strategies.
It seems that it is primarily the perceived usefulness and the effort expended that determine the subjective value attributed to a strategy.
Finally, further research is needed to investigate the factors influencing subjective values and whether these values represent habitual use of ER strategies by individuals.
